%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
	{#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
	\item\small{
    	{#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
  	\textbf{#1} & \textbf{\small #2} \\
  	\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  	\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
  	\small#1 & \textbf{\small }\\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
	{\Huge \scshape Pratyaksh Mehrotra} \\ \vspace{1pt}
	\small \raisebox{-0.1\height}\ +91 629 088 0586 ~ \href{mailto:pratyakshm.p@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{pratyakshm.p@gmail.com}} ~
	\href{https://linkedin.com/in/pratyakshm/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin}}
	\vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
	\resumeSubheading
  	{University of Engineering \& Management, Kolkata}{2021 -- 2025}
  	{Bachelor of Technology in Computer Science \& Engineering (CGPA of 8.7)}{Kolkata, India}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
  	{OPPO \& OnePlus}{2022'}
  	{Product Tester - Freelance}{Remote}
  	\resumeItemListStart
    \resumeItem{Conducted meticulous evaluation of over \textbf{5 prototypes} and hunted more than \textbf{500 bugs} (\textbf{70+ critical ones}) before they were released in the market, resulting in a significantly improved and stable user experience.}
    \resumeItem{Collaborated with cross-functional teams across the company, providing valuable feedback. Consistently ranked in \textbf{top 10} out of thousands of other \textbf{product testers} in South Asia region.}
    \resumeItem{Made serious contribution to OPPO's astounding Q1 2023 performance, resulting in a sharp \textbf{100\%} increase in user growth compared to Q1 2022, with sales skyrocketing from \textbf{13 million units} to an impressive \textbf{27 million units}.}
    \resumeItem{Spearheaded testing efforts for OPPO's latest flagship models, including the cutting-edge OPPO Reno 10 Pro+ 5G, ensuring optimal performance and user satisfaction.}
	\resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
	\vspace{-5pt}
	\resumeSubHeadingListStart
   	\resumeProjectHeading
      	{\textbf{WinRice} $|$ \emph{Git, PowerShell, YAML, Windows Registry, Automated Testing}  $|$ \underline{\href{https://github.com/pratyakshm/WinRice}{Source code}}}{2020 - present (3 yrs)}
      	\resumeItemListStart
        	\resumeItem{Engineered and crafted WinRice, a PowerShell script revolutionizing new Windows device setup, catering to a massive user base of \textbf{5000+ people}. It has gathered \textbf{300+ stars} on GitHub.}
            \resumeItem{Strengthened privacy and fortified security measures by systematically disabling non-essential tasks and eliminating superfluous apps and features.}
            \resumeItem{Worked with the open source community to develop and introduce new features based on user feedback.}
      	\resumeItemListEnd
       \vspace{-13 pt}
	\resumeProjectHeading
      	{\textbf{RevengeOS} $|$ \emph{Git, Bash, CI/CD, C, Makefile Java, Kotlin} $|$ \underline{\href{https://web.archive.org/web/20220109120922/https://revengeos.com/}{Website (archived)}}}{2020 - 2022 (2 yrs)}
      	\resumeItemListStart
        	\resumeItem{Headed a dynamic team in successfully \textbf{developing and launching RevengeOS 4.1}, revolutionizing the Android aftermarket firmware landscape with its unparalleled consistency, performance, and elegant design.}
        	\resumeItem{Garnered an impressive global user base with over \textbf{600K unique downloads}, demonstrating the widespread adoption and acclaim for RevengeOS.}
            \resumeItem{Amplified brand recognition and engagement through a visually stunning UI, driving over \textbf{1 million website visits} and capturing user interest.}
            \resumeItem{Re-established RevengeOS as a top player in the Android custom firmware community, attaining remarkable success with the release of versions 4.0 and 4.1, solidifying our position in the arena.}
            \resumeItem{\textbf{Developed RevengeOS for Xiaomi Redmi 5} (codename: rosy), delivering a seamless experience to a large user base across the globe.}
            \resumeItem{Elevated the Android experience for aftermarket firmware users by optimizing memory management, extending battery life, and enhancing device performance, surpassing the capabilities of MIUI.}
      	\resumeItemListEnd

	   \vspace{-13pt}
       \resumeProjectHeading
      	{\textbf{FlameGApps} $|$ \emph{Git, Bash, CI/CD}  $|$ \underline{\href{https://flamegapps.github.io/}{Website}}}{ 2019 - present (4 yrs)}
      	\resumeItemListStart
            \resumeItem{FlameGApps is a firm and consistent player in the Android scene. We’ve continued to ship updated GApps for Android 10, 11 and 12 as soon as they went GA.}
        	\resumeItem{Served as the Co-Founder of a custom Google Apps package project which is now widely popular among the global Android aftermarket firmware scene, with over \textbf{1.7 million} downloads.}
            \resumeItem{Used feedback to drive build quality and improve user experience.}
            \resumeItemListEnd
	\resumeSubHeadingListEnd
\vspace{-15pt}

%

%-----------Activities-----------
\section{Activities}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\resumeItemListStart
        \resumeItem{Got a \underline{\href{https://www.credly.com/badges/784601b7-0eed-4f17-a87e-19077df232da/public_url}{Microsoft certificate in the Security, Compliance, and Identity Fundamentals}} category, showcasing expertise by achieving an \textbf{outstanding score of 890/1000} on the SC-900 exam.}
    	\resumeItem{\textbf{Winner} in \textbf{Design and Aesthetic category} at the esteemed Bay Area Hacks hackathon, competing against a diverse field of over \textbf{400 participants}.}
        \resumeItem{Student Partner at Nothing Technology Limited.}
        \resumeItem{Cloud \& DevOps Lead at Google Developer Student Clubs, UEMK, 2023-24.}
        \resumeItem{Incoming Microsoft Learn Student Ambassador.}
  	\resumeItemListEnd
 \end{itemize}
 \vspace{-16pt}

%
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
 	\textbf{Languages}{: Bash, PowerShell, Python, Go, YAML, C\#, Java, HTML, CSS, JavaScript  \\
 	\textbf{Technologies/Frameworks/Libraries}{: Git, Linux, CI/CD, Docker, GitOps, Azure, GCP, AWS, ReactJS, React Router, Redux, Figma } \\
	}}
 \end{itemize}
 \vspace{-16pt}

\end{document}



